Network Cascades

### 2016-08-25 paper/paper.tex
Alter the ets

An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts in his paper below).

>>>>

An introduction to generating functions can be found in \cite{wilf1994generatingfunctionology} (this version of the book is referenced by Watts et. al. in his paper below).
